---
title: "Unit - I ggplot2 Assignment"
author: "FAREEDUL ASLAM P"
date: "23/9/2022"
output: html_document
---

### ASSIGNMENT QUESTIONS AND SOLUTIONS

#### Introduction Exercises:  

QUESTION 1:

What happens if you make a scatterplot of class versus drv? Why is the plot not useful?

```{r}
            ggplot(mpg, aes(x=class,y=drv))+
                geom_point()
```
The plot is not useful because the variable drv and class are categorical variables.

QUESTION 2:

What’s gone wrong with this code? Why are the points not blue?
ggplot(data = mpg) + 
geom_point(mapping = aes(x = displ, y = hwy, color = "blue"))

ANSWER : The points are not blue because the parameter color is included with aesthetic.If color is placed outside
displays the points in blue color.

```{r}
              ggplot(data = mpg) + 
geom_point(mapping = aes(x = displ, y = hwy), color = "blue")
```
QUESTION 3:

a)	What happens if you map a aesthetic to something other than a variable name, like aes(colour = displ < 5)?                                                    
```{r}
              ggplot(data=mpg)+
geom_point(aes(x = displ,y = hwy,color = displ<5))
```
b)	What does the stroke aesthetic do? What shapes does it work with?

```{r}
                     ggplot(data=mpg)+
geom_point(mapping = aes(x = displ,y = hwy),stroke=3)
```
Stroke is used to adjust the border size for shapes.It work with points (geom_point) shape.

QUESTION 4:

Read? Facet_wrap. What does nrow do? What does ncol do? What other options control the layout of the individual panels? Why doesn’t facet_grid() have nrow and ncol variables?

ANSWER : The arguments nrow (ncol) determines the number of rows (columns) to use when laying out the facets. It is necessary since facet_wrap() only facets on one variable.

The nrow and ncol arguments are unnecessary for facet_grid() since the number of unique values of the variables specified in the function determines the number of rows and columns.

QUESTION 5:

a)	What plots does the following code make? What does . do?  
ggplot(data = mpg) + 
geom_point(mapping = aes(x = displ, y = hwy)) +
facet_grid(drv ~ .)

```{r}
ggplot(data = mpg)+
  geom_point(mapping=aes(x=displ,y=hwy))+facet_grid(. ~ cyl)

```
b)	When using facet_grid() you should usually put the variable with more unique levels in the columns. Why?            
ANSWER : here will be more space for columns if the plot 
is laid out horizontally (landscape)

QUESTION 6:

What geom would you use to draw a line chart? A boxplot? A histogram? An area chart?

  ANSWER : linechart:geom_line()
          box plot:geom_boxplot()
          histogram:geom_histogram()
          area chart:geom_area()
QUESTION 7:

Will these two graphs look different? Why/why not?
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
     geom_point() +
     geom_smooth()
ggplot() +
     geom_point(data = mpg, mapping = aes(x = displ, y = hwy)) +
     geom_smooth(data = mpg, mapping = aes(x = displ, y = hwy))
     
ANSWER :  No,the two graphs looks similar.because both geom_point() and geom_smooth()
use same data and mappings

     
QUESTION 8:

 What does geom_col() do? How is different to geom_bar()?
 
  ANSWER :  The geom_col() function has different default stat than geom_bar(). The default stat of geom_col() is stat_identity(), which leaves the data as is. The geom_col() function expects that the data contains x values and y values which represent the bar height.

The default stat of geom_bar() is stat_count(). The geom_bar() function only expects an x variable. The stat, stat_count(), preprocesses input data by counting the number of observations for each value of x. The y aesthetic uses the values of these counts.

QUESTION 9:

What is the default geom associated with stat_summary()? How could you rewrite the previous plot to use that geom function instead of the stat function?

```{r}
ggplot(data = mpg, mapping =aes(x =cty, y =hwy)) +
geom_point() 
```
QUESTION 10:

What does the plot below tell you about the relationship between city and highway mpg? Why is coord_fixed() important? What does geom_abline() do?
ggplot(data = mpg, mapping =aes(x =cty, y =hwy)) +
geom_point() +
geom_abline() +
coord_fixed()

```{r}
  ggplot(data = mpg, mapping =aes(x =cty, y =hwy)) +
geom_point() +
geom_abline() +
coord_fixed()


```



